---
title: "Alcohol vs Seat choice"
author: "Jamal Evans"
date: "Spring 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

# Introduction

Data are from UCDavis.csv
Is the amount of alcohol consumed per week different for the different seating rows?

$H_0$: There is no difference per week between the different seating rows.

$H_A$: There IS a difference between alcohol consumption between different rows!

# Methods

We predict alcohol consumption based on row
Alcohol ~ Seat

Alcohol is a numeric variable
Seat is a categorical variable

so we use the num~cat file.

#description
## graphical description


## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```
 
 This boxplot shows the numerical data of alcohol consumed for back, front, and middle seats
 
## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
Numerical Summary shows that median for Back seat consumption is 3.5, Front seat consumption 0.0, and Middle seat consumption of 1.0 

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The P value is 0.000116 which is < 0.05. That means that students in all the rows do NOT consume the same amount of alcohol.


```{r}
plot(TukeyHSD(model1))
```
The HSD model shows that the people seated in the back row drink more than the people sitting in the middle and front rows. There is no evidence between alcohol consumtion between the middle and front row.

## Conclusions



