---
title: "Alcohol vs Seat choice"
author: "Jamal Evans"
date: "Spring 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

# Introduction

Data are from UCDavis.csv
Is the amount of alcohol consumed per week different for the different seating rows?

$H_0$: There is no difference per week between the different seating rows.

$H_A$: There IS a difference between alcohol consumption between different rows!

# Methods

We predict alcohol consumption based on row
Alcohol ~ Seat

Alcohol is a numeric variable
Seat is a categorical variable

so we use the num~cat file.

#description
## graphical description


## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```
 
 This boxplot shows the numerical data of alcohol consumed for back, front, and middle seats
 
## Numerical Summarys 



## Inferential Tests



## Conclusions


